%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{url}
\usepackage{hyperref}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Chunyin, SIU (Alex)} % Your name
\address{Brain Dynamics Lab, 1520 Page Mill Rd, Palo Alto, CA 94304}
\address{
\url{siuc@stanford.edu} \\
\url{https://c-siu.github.io}
}
% Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
%\address{} % Your phone number and email

\usepackage[T1]{fontenc}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Cornell University}, Ithaca, NY \hfill
{\em 2019 -- 2024} \\
PhD Applied Mathematics; supervised by Prof Gennady Samorodnitsky

{\bf The Chinese University of Hong Kong (CUHK)}, Hong Kong \hfill
{\em 2017 -- 2019} \\
MPhil Mathematics; supervised by Prof Ronald Lui %\\ \hfill { Overall Percentage: 68.14 }
%Thesis:
%Image Segmentation with Partial Convexity Prior Using Discrete Conformality Structures

{\bf The Chinese University of Hong Kong (CUHK)}, Hong Kong \hfill
{\em 2013 -- 2017} \\
BSc Mathematics; Minor in Economics %\hfill {cumulative GPA: 3.81/4.00} \\


%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

\iffalse
\begin{rSection}{Research Interests}
 Topological Data Analysis, Stochastic Topology, Network Analysis, Computational Geometry
\end{rSection}
%\begin{rSection}{Carrier Objective}
% To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
%\end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\fi

\begin{rSection}{Employment}

{\bf Postdoctoral Scholar, Stanford University School of Medicine} \hfill
{\em 2024 -- present} \\
%affiliate hosted by Dr Dmitriy Morozov; funded by the NSF MSGI program\\
develop topological-statistical techniques to analyze neuroimaging data

{\bf Affiliate, Lawrence Berkeley National Laboratory} \hfill
{\em Summer 2023} \\
%affiliate hosted by Dr Dmitriy Morozov; funded by the NSF MSGI program\\
build a neural network to predict the adsorption loadings of zeolite crystals with their topological features\\
verify a conjecture on the universality of a topological statistic of scientific datasets.

\end{rSection}


\begin{rSection}{Publications}

\emph{$\diamond$ indicates alphabetically-sorted author list. Superscripts indicate career stages (UnderGraduate, Graduate Student, or Professor).}

\begin{itemize}[noitemsep]
    \item \underline{C. Siu {\textsuperscript{GS}}}. \href{https://epubs.siam.org/doi/10.1137/24M1693179}{"The Topological Behavior of Preferential Attachment Graphs"}. \emph{SIAM Journal on Applied Algebra and Geometry}, 2025.

    \item \underline{C. Siu {\textsuperscript{GS}}}, G. Samorodnitsky \textsuperscript{P}, C. Yu \textsuperscript{P}, and R. He \textsuperscript{UG}. \href{https://www.cambridge.org/core/journals/advances-in-applied-probability/article/asymptotics-of-the-expected-betti-numbers-of-preferential-attachment-clique-complexes/5A7074FC4F88DFDD609655A80B26C055}{"The Asymptotics of the Expected Betti Numbers of Preferential Attachment Clique Complexes"}. \emph{Advances in Applied Probability}, 2025.
    
    \item \underline{C. Siu {\textsuperscript{GS}}}, G. Samorodnitsky \textsuperscript{P}, C. Yu \textsuperscript{P}, and A. Yao \textsuperscript{UG}. \href{https://rdcu.be/dCXLa}{"Detection of Small Holes by the Scale-Invariant Robust Density-Aware Distance (RDAD) Filtration"}. \emph{Journal of Applied and Computational Topology}, 2024.
    
    \item[$\diamond$] \underline{C. Siu {\textsuperscript{GS}}}, and R. Strichartz \textsuperscript{P}. \href{https://ems.press/journals/jfg/articles/10964400}{"Geometry and Laplacian on Discrete Magic Carpets"}. \emph{Journal of Fractal Geometry}, 2023.
    
    \item H. Law {\textsuperscript{GS}}, \underline{C. Siu {\textsuperscript{GS}}}, and R. Lui \textsuperscript{P}. \href{https://doi.org/10.1007/s10915-021-01569-x}{"Decomposition of Longitudinal Deformations via Beltrami Descriptors"}. \emph{Journal of Scientific Computing}, 2021.
    
    \item \underline{C. Siu {\textsuperscript{GS}}}, H.L. Chan {\textsuperscript{GS}}, and R. Lui \textsuperscript{P} \href{https://doi.org/10.1137/19M129718X}{"Image Segmentation with Partial Convexity Shape Prior Using Discrete Conformality Structures"}. \emph{SIAM Journal on Imaging Sciences}, 2020.
    
    \item[$\diamond$] J. Li \textsuperscript{UG}, and \underline{C. Siu \textsuperscript{UG}}. \href{https://arxiv.org/abs/1610.00898}{"An Elementary Approach on Left-Orderability, Cables of Torus Knots and Dehn Surgery"}. Preprint.
\end{itemize}

%{\bf Topological Statistics} \hfill {\em spring 2019 -- present}\\
% develop persistence tools to highlight small high-density features in data sets\\
% under the supervision of Prof Gennady Samorodnitsky and Prof Christina Yu
% \iffalse
%\begin{itemize}
%    \item develop statistical foundation for inference of qualitative topological features of a data set
%    \item under the supervision of Prof Gennady Samorodnitsky and Prof Christina Yu
%\end{itemize}
%\fi

%{\bf HJB Equation and Time-Inconsistent Planning} \hfill {\em fall 2019 -- present}\\
%study the behavior of a present-biased planner, such as plan modification and procrastination\\
%bound the cost of present bias by the range of cost and the strength of bias\\
%supervised by Prof Alexander Vladimirsky
%\iffalse
%\begin{itemize}
%    \item study the behavior of a present-biased planner, such as plan modification and procrastination
%    \item bounded the cost of present bias by the range of cost and the strength of bias
%    \item supervised by Prof Alexander Vladimirsky
%\end{itemize}
%\fi

%{\bf Image Segmentation with Convexity Shape-Prior} \hfill {\em fall 2018 -- summer 2019}\\
%    developed an image segmentation algorithm with convexity guarantee using quasi-conformal geometry\\
%    joint work with Hei-Long Chan under the supervision of Prof Lok-Ming Lui\\
%    published at {SIAM Journal on Imaging Sciences}\\
%    doi: \href{https://doi.org/10.1137/19M129718X}{0.1137/19M129718X}
%    \iffalse
%\begin{itemize}
%    \item developed an image segmentation model that guarantees the convexity of the segmented region by quasi-conformal geometry
%    \item joint work with Hei-Long Chan under the supervision of Prof Lok-Ming Lui
%    \item published at SIAM Journal on Imaging Sciences 
%\end{itemize}
%\fi

%{\bf Analysis on Fractals} \hfill {\em summer 2016}\\
%proved the growth rate of ball sizes on the fractals IMC and studied the Laplacian on them\\
%joint work with Eric Goodman under the supervision of Prof Robert Strichartz\\
%accepted by Journal of Fractal Geometry 
%\iffalse
%\begin{itemize}
%    \item proved the growth rate of ball sizes on the fractal \emph{infinite magic carpet} and studied the Laplacian on them.
%    \item joint work with Eric Goodman under the supervision of Prof Robert Strichartz
%    \item submitted to Journal of Fractal Geometry 
%\end{itemize}
%\fi

\end{rSection}

%----------------------------------------------------------------------------------------
%	HONORS
%----------------------------------------------------------------------------------------

\begin{rSection}{Select Awards and Honors}

\href{https://scholars.croucher.org.hk/scholars/siu-chun-yin}{\textbf{Croucher Fellowship for Postdoctoral Research}} \hfill {\em 2024/2025}\\
Annually, 6 -- 10 Hong Kong scholars pursuing overseas postdoctoral research in science are selected.
% Award amount: 2 years of stipend (USD 63000 / year) and fringe benefits

\href{https://scholars.croucher.org.hk/scholars/siu-chun-yin}{\textbf{Croucher Scholarship for Doctoral Study}} \hfill {\em 2019/2020}\\
Annually, 9 -- 16 Hong Kong scholars pursuing overseas doctoral degrees in science are selected.
%Award amount: 3 years of stipend (USD 30300 / year) and fringe benefits
%{\footnotesize{Annually, 9 -- 16 Hong Kong scholars pursuing an overseas doctoral degree in science, medicine or technology are selected.}}

\href{https://www.wfsfaa.gov.hk/sfo/seymf/en/index.htm}{\textbf{Sir Edward Youde Memorial Fellowship (for Postgraduate Research Students)}} \hfill {\em 2017/2018}\\
Annually, 3 -- 5 Hong Kong fellows are selected among nominees from local institutions.
%Award amount: one-off grant of HKD 50000 (USD 6370)
%{\footnotesize{Annually, 3 -- 5 fellows in Hong Kong are selected from the postgraudate students nominated by the heads of their institutions.}}

\href{https://www.math.cuhk.edu.hk/student-centre/scholarships/best-teaching-assistant-award}{\textbf{Best Teaching Assistant Award at CUHK Math}} \hfill {\em 2018/2019}\\
Annually, 3 teaching assistants in the Department of Mathematics at CUHK receive this award.
%Award amount: ​​HKD 5000 (USD637)
%{\footnotesize{Annually, 3 teaching assistants in the Department of Mathematics at CUHK receive this award.}}

\end{rSection}

\newpage

\begin{rSection}{Invited Talks}

"Random Topology: The Topology of Preferential Attachment Graphs". Probability Seminar. Stanford University, CA, Jun 2025.

"Random Topology: The Topology of Preferential Attachment Graphs". Probability Seminar. Northwestern University, IL, Feb 2025.

"Homology and Homotopy Properties of Scale-Free Networks". Applied Algebraic Topology Research Network (AATRN) Networks Seminar. Virtual, Feb 2025.

"Detecting Weak Topological Signals in Noisy Environments". Hot Topics in Data Science. University at Buffalo, NY (Virtual), Feb 2024.

"Homology and Homotopy Properties of Scale-Free Networks". University of Florida Topological Data Analysis conference. University of Florida, FL, Feb 2024.

"The Expected Betti Numbers of Preferential Attachment Clique Complexes". Applied Topology Seminar. Oxford University, Britain (Virtual), Nov 2023.

"The Asymptotics of the Expected Betti Numbers of Preferential Attachment Clique Complexes". Applied Algebraic Topology Research Network (AATRN) Online Seminar. Virtual, Nov 2023.

"The Topology of Preferential Attachment Graphs". Probability and Statistical Physics Seminar. Chicago University, IL, Oct 2023.

"The Topology of Preferential Attachment Graphs". Probability Seminar. Purdue University, IN, Sep 2023.

"The Topology of Preferential Attachment". Seminario Doctorado, Actividad del Programa de Doctorado "Mathematicas". University of Seville, Spain, Sep 2023.

"The Topology of Preferential Attachment Graphs". Probability and Applications Seminar. Queen Mary University of London, Britain, Sep 2023.

"Detection of Small Topological Features by the Scale-Invariant Robust Density-Aware Distance (RDAD) Filtration". CUHK, Hong Kong, Jan 2023.

\end{rSection}


\begin{rSection}{Contributed Talks}

The Topology of Preferential Attachment Clique Complexes

\begin{itemize}[noitemsep]
    \item SIAM Applied Algebraic Geometry Conference, University of Wisconsin-Madison, WI, Jul 2025.
    \item Northeast Probability Seminar, New York University, NY, Nov 2023
    \item Binghamton University Graduate Combinatorics, Algebra and Topology. Binghamton University, NY, Nov 2023.
    \item Computation Persistence Workshop. Purdue University, IN, Sep 2023.
    \item Geometry and Topology meet Data Analysis and Machine Learning. Northeastern University, MA, Jun 2023.
    \item Finger Lakes Probability Seminar. Binghamton University, NY, Feb 2023.
\end{itemize}

Detecting Weak Topological Signals in Noisy Environment

\begin{itemize}[noitemsep]
    \item Computation Persistence Workshop. Graz University of Technology, Graz, Austria (Virtual), Sep 2024.
    \item Joint Statistical Meetings. Toronto, Canada, Aug 2023.
    \item Binghamton University Graduate Combinatorics, Algebra and Topology. Binghamton University, NY, Nov 2022.
    \item 3rd Upstate New York Topology Seminar. Syracuse University, NY, Oct 2022.
\end{itemize}
\end{rSection}

\newpage

\begin{rSection}{Poster Presentations}
The Topology of Preferential Attachment Clique Complexes
\begin{itemize}[noitemsep]
    \item Mid-Atlantic Topology Conference, Northeastern University, MA, Mar 2024
    \item Randomness in Topology and its Applications. The University of Chicago, IL, Mar 2023.
\end{itemize}

Detecting Weak Topological Signals in Noisy Environment

\begin{itemize}[noitemsep]
    \item Algebraic Topology, Methods, Computation and Science 10. Oxford University, Britain, Jun 2022.
    \item Bridging Applied and Quantitative Topology. Virtual, May 2022.
    \item AATRN Poster Session. Virtual, Oct 2021.
\end{itemize}
\end{rSection}

\begin{rSection}{Professional Services}
reviewer for the \emph{Nature Scientific Reports} \hfill {\em Spring 25}\\
reviewer for the \emph{Mathematical Reviews} \hfill {\em Spring 25 -- present}\\
reviewer for the \emph{Electronic Journal of Probability} \hfill {\em Fall 24}\\
reviewer for \emph{Homology, Homotopy and Applications} \hfill {\em Fall 23}\\
student representative of the Colloquium Committee, CAM, Cornell \hfill {\em Fall 23 -- Spring 24} \\
officer of SIAM Student Chapter, Cornell \hfill {\em Fall 22 -- Spring 24}
\end{rSection}

\begin{rSection}{Teaching Experiences}

MATH 1920 
Multivariable Calculus for Engineers, Cornell, head teaching assistant \hfill {\em Spring 23}\\
MATH 1920 
Multivariable Calculus for Engineers, Cornell, teaching assistant \hfill {\em Fall 22}\\
%Directed Reading Program on Applied Topology, Cornell, mentor \hfill {\em Fall 20, Spring 21, Spring 22}\\
MATH 2020 Advanced Calculus II, CUHK, teaching assistant \hfill {\em Spring 19}\\
MATH 4060 Complex Analysis, CUHK, teaching assistant \hfill {\em Fall 18}\\
EPYMT Number Theory and Cryptography, CUHK, teaching assistant \hfill {\em Summer 18}\\
MATH 2010 Advanced Calculus I, CUHK, teaching assistant \hfill {\em Spring 18}\\
MATH 1510 Calculus for Engineers, CUHK, teaching assistant \hfill {\em Spring 18}\\
MATH 1540 University Mathematics for Financial Studies, CUHK, teaching assistant \hfill {\em Fall 17}
\end{rSection}



\begin{rSection}{Mentorship Experiences}


\href{https://www.linkedin.com/in/avhan-misra/}{\textbf{Avhan Misra}}, currently Rice PhD student \hfill {\em Fall 23 -- Summer 24} \\
Undergraduate Research Assistant, cosupervised by Gennady Samorodnitsky

\href{https://www.linkedin.com/in/rongyi-caroline-he}{\textbf{Rongyi He}}, currently Quant and Data at Trexquant Investment LP \hfill {\em Summer 22 -- Summer 23} \\
Undergraduate Research Assistant, cosupervised by Gennady Samorodnitsky

\href{https://www.linkedin.com/in/luis-hoderlein-6a501119a/}{\textbf{Luis Hoderlein}}, currently Yale PhD student \hfill {\em Spring 22 -- Summer 22} \\
Undergraduate Directed Reading Program on dimension reduction and UMAP

\textbf{James Zhang} \hfill {\em Summer 22} \\
Undergraduate Directed Reading Program on Erdos-Renyi graphs

\textbf{Tom Shi} \hfill {\em Spring 22} \\
Undergraduate Directed Reading Program on ranking of graph data

\href{https://andreyyao.github.io/}{\textbf{Andrey Yao}}, currently Madison PhD student \hfill {\em Fall 20 -- Spring 22}\\
Undergraduate Directed Reading Program on computational topology\\
Undergraduate Research Assistant, cosupervised by Gennady Samorodnitsky

\end{rSection}



\begin{rSection}{Additional Information}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Natural languages & English, Chinese (Cantonese, Mandarin) \\
Programing & MATLAB, Python, Bash, R
\end{tabular}
\end{rSection}

\iffalse
\newpage
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Modeling and Analysis \ & AutoCad, Revit, StaadPro \\
Software \& Tools & MS Office, Latex \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{SJ Contracts, Pune}{June 2016}{Site Engineer}{}
\item On-site internship under this leading construction company. Learned and implemented various aspects such as quantity estimation, labour management and safety precautions.
\end{rSubsection}


\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Achievements} 
 Runners up in B.G.Shirke Vidyarthi Competition for Innovative Project organized by Pune Construction Engineering Research Foundation in January 2018
\item Won First Prize in Model Making Competition Organized by Symbiosis Institute of Technology, Pune.
\end{rSection}

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Cirrucular} \itemsep -3pt
\item Co-Organized “ Nirmitee 2017” - a National Symposium of Civil Department of MIT, Pune
\item Attended a workshop on Autodesk Revit at IIT Bombay in 2014.
\item Winner of Inter Departmental Football Competition 2015.
\item Member of the  Rotaract Club Of Pune Pride from 2014 to 2017.
\item Worked for a start-up company Named OUST as a Regional Marketing Manager
%\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
 %\item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
 %\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
 %\item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %

\end{rSection}

\begin{rSection}{Personal Traits}
\item Highly motivated and eager to learn new things.
\item Strong motivational and leadership skills.
\item Ability to work as an individual as well as in group.
\end{rSection}
\fi

\end{document}
