%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{url}
\usepackage{hyperref}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Chunyin, SIU (Alex)} % Your name
\address{657 Rhodes Hall, Cornell University, Ithaca, NY 14853}
\address{
\url{cs2323@cornell.edu} \\
\url{https://c-siu.github.io}
}
% Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
%\address{} % Your phone number and email

\usepackage[T1]{fontenc}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}

\emph{* denotes entries with alphabetically listed authors.}

\underline{C. Siu}, G. Samorodnitsky, C. Yu, and R. He. \href{https://arxiv.org/abs/2305.11259}{"The Asymptotics of the Expected Betti Numbers of Preferential Attachment Clique Complexes"}. Submitted.

\underline{C. Siu}, G. Samorodnitsky, C. Yu, and A. Yao. \href{https://arxiv.org/abs/2204.07821}{"Detection of Small Holes by the Scale-Invariant Robust Density-Aware Distance (RDAD) Filtration"}. Submitted.

* \underline{C. Siu}, and R. Strichartz. \href{https://ems.press/journals/jfg/articles/10964400}{"Geometry and Laplacian on Discrete Magic Carpets"}. \emph{Journal of Fractal Geometry}, 2023.

H. Law, \underline{C. Siu}, and R. Lui. \href{https://doi.org/10.1007/s10915-021-01569-x}{"Decomposition of Longitudinal Deformations via Beltrami Descriptors"}. \emph{Journal of Scientific Computing}, 2021.

\underline{C. Siu}, H.L. Chan, and R. Lui \href{https://doi.org/10.1137/19M129718X}{"Image Segmentation with Partial Convexity Shape Prior Using Discrete Conformality Structures"}. \emph{SIAM Journal on Imaging Sciences}, 2020.

* J. Li, and \underline{C. Siu}. \href{https://arxiv.org/abs/1610.00898}{"An Elementary Approach on Left-Orderability, Cables of Torus Knots and Dehn Surgery"}. Preprint.

\end{rSection}
\end{document}
